Sequential rank agreement methods for comparison of ranked lists

### 2016-02-24 latex/paper.Rnw
start of new section for review: change point analysis

>>>>

\section{Change-point analysis}

In many applications it is of interest to estimate a list depths which
satisfies a change point criterion. In this section we investigate the
theoretical properties of our proposed method for this specific
task. As Hall and Schimek, we work with an infinite set of lists
\mathcal{L} and study the asymptotic behaviour for
$L\to\infty$. However, we do not allow the length of the lists to
change with $L$ as in most applications the length of the lists is
fixed [FIXME: for finite $L$ are there only finitely many forskelige
lists (aber dass stoert keinen grossen geist, siger karlsson)]. First,
we define the parameter of interest. For any given threshold value $q$
a change-point $d_0(q)$ in the list agreement is defined by
\begin{equation*}
  d_0=\textrm{arginf}_{d\in\{1,\dots,L\}}\textrm{sra}(d)>q.
\end{equation*}
The value of $q$ could for example be the agreement of randomly
permuted lists [FIXME: there is only one SRA value for infinitely many
random permutations, no skygge!].

The theorem shows consistency of the plug-in estimate of
\begin{equation*}
\hat{d_0} = \textrm{arginf}_{d\in\{1,\dots,L\}}\widehat{\textrm{sra}}(d)>q
\end{equation*}
[FIXME: $\textrm{sra}$ -> $\widehat{\textrm{sra}}$ in rest of article?]
\begin{theorem}
  $\hat{d_0}\overset{L\to\infty}{\longrightarrow}d_0$
\end{theorem}

Proof: We rewrite the square of the sequential rank agreement \eqref{def:sra} as
\begin{equation}
(\textrm{sra}(d))^2= \sum_{p=1}^P \sum_{l=1}^L 1\{R_l(X_p)\le d\}\sum_{p=1}^P(1-\prod_{l=1}^L 1\{R_l(X_p)>d\}) A(X_p)^2
\end{equation}
[FIXME: Andreas details the proof with Cauchy-Schwarz.]
[FIXME: Det er lidt kedelig for saadan en fin en som Andreas: Skal theoremet og bevis ikke vaere for en general agreement metric, ikke nodvendigvis den i equation (2), og kan vi charakterisere hvad den skal opfylde?]
